Decomposing labelled proof theory\\ for intuitionistic modal logic

### 2018-05-01 WiL.tex
minor things

%% Title information
\title{Decomposing labelled proof theory\\for intuitionistic modal logic}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

\sonia{Removed paragraph. Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}
%For sequent systems for intuitionistic logics there is always a choice
%to be made: make the system \emph{single conclusion} following
%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
%variant because of the closer correspondence to the semantics. In that
%respect, our system is closer to~\cite{kuz:str} than
%to~\cite{Simpson} and~\cite{mar:str}.

\section{Preliminaries\todo{give a more informative title}}

>>>>

%% Title information
\title[Decomposing labelled proof theory for intuitionistic modal logic]{Decomposing labelled proof theory\\ for intuitionistic modal logic}         $$[Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

\sonia{Removed paragraph. Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}\lutz{maybe, but getting all the theorems right is not so easy, we had a hard time in the nested variant}

For sequent systems for intuitionistic logics there is always a choice
to be made: make the system \emph{single conclusion} following
Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
variant because of the closer correspondence to the semantics. In that
respect, our system is closer to~\cite{kuz:str} than
to~\cite{Simpson} and~\cite{mar:str}.

\section{Preliminaries on intuitionistic modal logics}
